Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
make TODOs in red in introduction.

Currently, x\% of users fail and with the current interface for reasons a, b, and c. Of those that do succeed, the average time to completion is y. This can lead to a bad user experience, users quitting Tor, or causing high-risk users to make mistakes. With the new design, only x'\% of users fail to configure successfully and the average time to completion is y'. Tor has already implemented some of these changes.

>>>>

Currently, {\color {red} TODO}\% of users fail and with the current interface for reasons {\color {red} TODO}, {\color {red} TODO}, and {\color {red} TODO}. Of those that do succeed, the average time to completion is {\color {red} TODO}. This can lead to a bad user experience, users quitting Tor, or causing high-risk users to make mistakes. With the new design, only {\color {red} TODO}\% of users fail to configure successfully and the average time to completion is {\color {red} TODO}. Tor has already implemented some of these changes.
